Supporting Information

### 2022-03-29 Manuscript/Supplementary_Material/Specialization_trophic_guild.Rmd
specialization added to supp. mat

```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.width=14,fig.height=6, out.width='100%'}

@@

pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",line.par = list(col = 'black'),
                         strip.names=c("Bee",
                                       "Coleoptera",
                                       "Lepidoptera",
                                       "Non-bee-Hymenoptera",
                                       "Non-syrphids-diptera",
                                       "Syrphids"),gg = TRUE) + theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8)

plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",
       strip.names=c("Selfing herbs",
                     "Small outcrossing perennials",
                     "Self-incompatible perennials\nwith large flowers",
                     "Tall plants with small\nunisexual flowers",
                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))

library(patchwork)
pollinators_sp_plot/plants_sp_plot & theme(axis.text=element_text(size=10),
        axis.title=element_text(size=14)) & plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%'}

@@

pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",line.par = list(col = 'black'),
                         strip.names=c("Bee",
                                       "Coleoptera",
                                       "Lepidoptera",
                                       "Non-bee-Hymenoptera",
                                       "Non-syrphids-diptera",
                                       "Syrphids"),gg = TRUE) + theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8) +
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
    ggtitle("Floral visitors")

plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",
       strip.names=c("Selfing herbs",
                     "Small outcrossing perennials",
                     "Self-incompatible perennials\nwith large flowers",
                     "Tall plants with small\nunisexual flowers",
                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
  ggtitle("Plants")

library(patchwork)
pollinators_sp_plot/plants_sp_plot & theme(axis.text=element_text(size=10),
        axis.title=element_text(size=16)) & plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))

### 2022-03-29 Manuscript/Supplementary_Material/Supporting_information_Functional_Ecology.Rmd
edits
specialization added to supp. mat

**The non-random assembly of functional motifs in plant-pollinator networks worldwide**

Jose B. Lanuza, Alfonso Allen-Perkins and Ignasi Bartomeus

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12, fig.align = 'center', fig.cap="\\textbf{Figure S6.} Association between the frequency and specificity on the different motif positions for floral visitor (panel A) and plant (panel B) groups. The different numerical categories of the plant groups correspond to: 1 (selfing herbs), 2 (small outcrossing perennials), 3 (self-incompatible perennials with large flowers), 4 (tall plants with small unisexual flowers) and 5 (short-lived outcrossers with long zygomorphic flowers)."}

library(ggplot2)
library(patchwork)

pollinator_means_reordered_s_1 <- read.csv("../../Data/Csv/pollinator_means_reordered_s_1.csv")

plant_means_s <- read.csv("../../Data/Csv/plant_means_s.csv")

p1 <- ggplot(pollinator_means_reordered_s_1,aes(x=s,y=mean))+
  geom_point(alpha=0.5, color="black")+
  geom_smooth(method = "lm",color="black")+
  facet_wrap(~Node_FG)+
  labs(x="Specificty",y="Average frequency per motif position") +
  theme_bw() + ggtitle("Floral visitors") +
  theme(plot.title = element_text(hjust = 0.5, size = 25),
        axis.text=element_text(size=12),
        axis.title=element_text(size=18),
        strip.text = element_text(size=20))

p2 <- ggplot(plant_means_s,aes(x=s,y=mean))+
  geom_point(alpha=0.5, color="black")+
  geom_smooth(method = "lm", color="black")+
  facet_wrap(~Node_FG)+
  labs(x="Specificty",y="Average frequency per motif position")+
  theme_bw() + ggtitle("Plants") +
  theme(plot.title = element_text(hjust = 0.5, size = 25),
        axis.text=element_text(size=12),
        axis.title=element_text(size=18),
        strip.text = element_text(size=20))

p1/p2 +  plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))

>>>>

**The non-random assembly of functional motifs in plant-pollinator networks**

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%'}

library(ggplot2)
library(glmmTMB)
#Read floral visitor data and model output
model_freq_specif_ind <- readRDS("../../Data/RData/model_freq_specif_ind.RData")
pollinator_freq_position_s_ind <- readRDS("../../Data/RData/pollinator_freq_position_s_ind.RData")
#Read plant data and model output
model_freq_specif_ind_plant <- readRDS("../../Data/RData/model_freq_specif_ind_plant.RData")
plant_freq_position_s_ind <- readRDS("../../Data/RData/plant_freq_position_s_ind.RData")

library(visreg)

# Pollinator Model REAL OUTPUTS!!!

pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",line.par = list(col = 'black'),
                         strip.names=c("Bee",
                                       "Coleoptera",
                                       "Lepidoptera",
                                       "Non-bee-Hymenoptera",
                                       "Non-syrphids-diptera",
                                       "Syrphids"),gg = TRUE) + theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8) +
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
    ggtitle("Floral visitors")

plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",
       strip.names=c("Selfing herbs",
                     "Small outcrossing perennials",
                     "Self-incompatible perennials\nwith large flowers",
                     "Tall plants with small\nunisexual flowers",
                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
  ggtitle("Plants")

library(patchwork)
pollinators_sp_plot/plants_sp_plot & theme(axis.text=element_text(size=10),
        axis.title=element_text(size=16)) & plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
